Appendix 3: Estimating species interactions

### 2015-08-04 Harris_2015/recovery.Rmd
almost done

---
output: 
  pdf_document:
    keep_tex: true
title: Appendix [[X]]":"" estimating species interactions
subtitle: \"Estimating species interactions from observational data with Markov networks\"
author: David J. Harris
fontsize: 11pt
---

This document describes how the different models were fit to the simulated data 
from Appendix [[XX]] and how each model's performance was evaluated.[^1]

@@

  ######## BayesComm and partial BayesComm ########
  bc = BC(Y = x, model = "community", its = 10)

@@

# ggplot(z[z$n_sites >0, ], aes(x = `Markov network`, y = truth)) + 
#   stat_binhex(bins = 100) + 
#   xlab("Estimated coefficient value") + 
#   ylab("\"True\" coefficient value") + 
#   stat_hline(yintercept = 0, size = 1/8) + 
#   stat_vline(xintercept = 0, size = 1/8) + 
#   scale_fill_gradient(low = "#F0F0F0", high = "darkblue", trans = "identity") +
#   stat_smooth(method = "lm", se = FALSE, size = 1) +
#   theme_bw()

ggplot(z[z$n_sites >0, ], aes(x = -`Pairs`, y = truth)) + 
  stat_binhex(bins = 100) + 
  xlab("Estimated coefficient value") + 
  ylab("\"True\" coefficient value") + 
  stat_hline(yintercept = 0, size = 1/8) + 
  stat_vline(xintercept = 0, size = 1/8) + 
  scale_fill_gradient(low = "#F0F0F0", high = "darkblue", trans = "identity") +
  stat_smooth(method = "lm", se = FALSE, size = 1) +
  theme_bw()
```

>>>>

---
output: 
  pdf_document:
    keep_tex: true
title: "Appendix 3: Estimating species interactions"
subtitle: \"Estimating species interactions from observational data with Markov networks\"
author: David J. Harris
fontsize: 11pt
---

This document describes how the different models were fit to the simulated data 
from Appendix 2 and how each model's performance was evaluated.[^1]

@@

  ######## BayesComm and partial BayesComm ########
  bc = BC(Y = x, model = "community", its = 1000)

@@

ggplot(z[z$n_sites >0, ], aes(x = `Markov network`, y = truth)) + 
  stat_binhex(bins = 100) + 
  xlab("Estimated coefficient value") + 
  ylab("\"True\" coefficient value") + 
  stat_hline(yintercept = 0, size = 1/8) + 
  stat_vline(xintercept = 0, size = 1/8) + 
  scale_fill_gradient(low = "#F0F0F0", high = "darkblue", trans = "identity") +
  theme_bw() + 
  ggtitle("Markov network") + 
  stat_abline(intercept = 0, slope = coef(lm(z$truth ~ z$`Markov network` + 0)))

ggplot(z[z$n_sites >0, ], aes(x = `Pairs`, y = truth)) + 
  stat_binhex(bins = 100) + 
  xlab("Estimated coefficient value") + 
  ylab("\"True\" coefficient value") + 
  stat_hline(yintercept = 0, size = 1/8) + 
  stat_vline(xintercept = 0, size = 1/8) + 
  scale_fill_gradient(low = "#F0F0F0", high = "darkblue", trans = "identity") +
  theme_bw() + 
  ggtitle("Null model (\"Pairs\")") + 
  stat_abline(intercept = 0, slope = coef(lm(z$truth ~ z$Pairs + 0)))
```
